### 2024-05-13 DP_MiroslavHajek/docs/firmware/latex/group__datalogger.tex
Thesis send to feedback

\begin{DoxyCompactList}\small\item\em Configuation of the recording button. \end{DoxyCompactList}\item 

@@

\begin{DoxyCompactList}\small\item\em Configuation of the indicator LED light. \end{DoxyCompactList}\end{DoxyCompactItemize}

@@

\begin{DoxyCompactList}\small\item\em Signal fatal error of system occuring by blinking indicator LED and halting execution. \end{DoxyCompactList}\end{DoxyCompactItemize}

@@

Signal fatal error of system occuring by blinking indicator LED and halting execution.

>>>>

\begin{DoxyCompactList}\small\item\em Configuration of the recording button. \end{DoxyCompactList}\item 

@@

\begin{DoxyCompactList}\small\item\em Configuration of the indicator LED light. \end{DoxyCompactList}\end{DoxyCompactItemize}

@@

\begin{DoxyCompactList}\small\item\em Signal fatal error of system indiacted by blinking LED and halting execution. \end{DoxyCompactList}\end{DoxyCompactItemize}

@@

Signal fatal error of system indiacted by blinking LED and halting execution.

### 2024-05-13 DP_MiroslavHajek/docs/firmware/latex/main_8c.tex
Thesis send to feedback

\doxysubsection{Firmware Tasks}
\hypertarget{group__main}{}\label{group__main}\index{Firmware Tasks@{Firmware Tasks}}

Main program of the firmware execution.

\doxysubsubsubsection*{Functions}
\begin{DoxyCompactItemize}
\item 
\Hypertarget{group__main_ga0ec5d28752074ca54a70acc838f672e4}\label{group__main_ga0ec5d28752074ca54a70acc838f672e4} 
void {\bfseries push\+\_\+trigger} (void \texorpdfstring{$\ast$}{*}args)
\begin{DoxyCompactList}\small\item\em Task to start or stop recoding after siganl from button press. \end{DoxyCompactList}\item 
\Hypertarget{group__main_gac6ec22d4c97c0c96e99f3379d88cc6c0}\label{group__main_gac6ec22d4c97c0c96e99f3379d88cc6c0} 
void {\bfseries read\+\_\+accelerometer} (void \texorpdfstring{$\ast$}{*}args)
\begin{DoxyCompactList}\small\item\em Task to read FIFO buffer of the accelerometer and write it to Queue. \end{DoxyCompactList}\item 
\Hypertarget{group__main_gaeec34572dd8cb6da1ffaa4e74db0bca4}\label{group__main_gaeec34572dd8cb6da1ffaa4e74db0bca4} 
void {\bfseries write\+\_\+card} (void \texorpdfstring{$\ast$}{*}args)
\begin{DoxyCompactList}\small\item\em Task to write accelerations vectors from Queue to the memory card. \end{DoxyCompactList}\item 
\Hypertarget{group__main_ga630544a7f0a2cc40d8a7fefab7e2fe70}\label{group__main_ga630544a7f0a2cc40d8a7fefab7e2fe70} 
void {\bfseries app\+\_\+main} (void)
\begin{DoxyCompactList}\small\item\em Entrypoint of firmware to setup hardware peripherals and run tasks. \end{DoxyCompactList}\end{DoxyCompactItemize}
\doxysubsubsubsection*{Variables}
\begin{DoxyCompactItemize}
\item 
\Hypertarget{group__main_ga4bfd79880585a6aa3c7110a75dc0c82a}\label{group__main_ga4bfd79880585a6aa3c7110a75dc0c82a} 
Task\+Handle\+\_\+t {\bfseries trigger\+\_\+task}
\begin{DoxyCompactList}\small\item\em Task handler for notification of button press. \end{DoxyCompactList}\item 
\Hypertarget{group__main_ga768ac04522700fd0788f959b1c7510cb}\label{group__main_ga768ac04522700fd0788f959b1c7510cb} 
Task\+Handle\+\_\+t {\bfseries sampler\+\_\+task}
\begin{DoxyCompactList}\small\item\em Task handler for notification from sampling timer. \end{DoxyCompactList}\item 
\Hypertarget{group__main_gaa6b473c01115f6c0fd05415b7ca3a287}\label{group__main_gaa6b473c01115f6c0fd05415b7ca3a287} 
Queue\+Handle\+\_\+t {\bfseries samples}
\begin{DoxyCompactList}\small\item\em Queue for sending samples from the sensor read task to the memory card write task. \end{DoxyCompactList}\item 
\Hypertarget{group__main_gaf04b0de520c6e42f039c5edf47b13dc2}\label{group__main_gaf04b0de520c6e42f039c5edf47b13dc2} 
spi\+\_\+device\+\_\+handle\+\_\+t {\bfseries spi}
\begin{DoxyCompactList}\small\item\em SPI bus handle. \end{DoxyCompactList}\item 
\Hypertarget{group__main_ga21408672a588f2b1db6f8f620eecbc59}\label{group__main_ga21408672a588f2b1db6f8f620eecbc59} 
stmdev\+\_\+ctx\+\_\+t {\bfseries sensor}
\begin{DoxyCompactList}\small\item\em Accelerometer sensor device. \end{DoxyCompactList}\item 
\Hypertarget{group__main_gad85cb86f6cbc94b88b09c3315c9028f1}\label{group__main_gad85cb86f6cbc94b88b09c3315c9028f1} 
sdmmc\+\_\+card\+\_\+t \texorpdfstring{$\ast$}{*} {\bfseries card} = NULL
\begin{DoxyCompactList}\small\item\em SD memory card handle. \end{DoxyCompactList}\item 
\Hypertarget{group__main_ga702945180aa732857b380a007a7e2a21}\label{group__main_ga702945180aa732857b380a007a7e2a21} 
FILE \texorpdfstring{$\ast$}{*} {\bfseries file} = NULL
\begin{DoxyCompactList}\small\item\em Currently opened file handle. \end{DoxyCompactList}\item 
\Hypertarget{group__main_ga94544252c41b06346dc45f70cbd48d63}\label{group__main_ga94544252c41b06346dc45f70cbd48d63} 
Semaphore\+Handle\+\_\+t {\bfseries file\+\_\+mutex}
\begin{DoxyCompactList}\small\item\em Mutex to protect file handle. \end{DoxyCompactList}\item 
\Hypertarget{group__main_gaf409115fcaa12619a90c9b581bafa64a}\label{group__main_gaf409115fcaa12619a90c9b581bafa64a} 
bool {\bfseries is\+\_\+recording} = false
\begin{DoxyCompactList}\small\item\em Flag for active recording in progress. \end{DoxyCompactList}\item 
\Hypertarget{group__main_gad70a27ce9ba8cfa78153904f05e38c44}\label{group__main_gad70a27ce9ba8cfa78153904f05e38c44} 
int32\+\_\+t {\bfseries sensor\+\_\+timestamp} = 0
\begin{DoxyCompactList}\small\item\em Last seen accelerometer timestamp. \end{DoxyCompactList}\item 
const esp\+\_\+timer\+\_\+create\+\_\+args\+\_\+t \mbox{\hyperlink{group__main_ga6bc19a77e2c149ca9b7e86d2ad25ef64}{sampler\+\_\+timer\+\_\+conf}}
\item 
\Hypertarget{group__main_ga5e17ddc2ef9d796aedaa59e618c49af1}\label{group__main_ga5e17ddc2ef9d796aedaa59e618c49af1} 
esp\+\_\+timer\+\_\+handle\+\_\+t {\bfseries sampler\+\_\+timer}
\begin{DoxyCompactList}\small\item\em Periodic timer to signal when to read FIFO buffer from accelerometer. \end{DoxyCompactList}\item 
const esp\+\_\+timer\+\_\+create\+\_\+args\+\_\+t \mbox{\hyperlink{group__main_gacb077cf1ef581c961e7e5222a98f6897}{stop\+\_\+timer\+\_\+conf}}
\item 
\Hypertarget{group__main_gab1d567cca0836a894a9577ba45fac511}\label{group__main_gab1d567cca0836a894a9577ba45fac511} 
esp\+\_\+timer\+\_\+handle\+\_\+t {\bfseries stop\+\_\+timer}
\begin{DoxyCompactList}\small\item\em Timer to stop recording after fixed amount of time. \end{DoxyCompactList}\end{DoxyCompactItemize}

\doxysubsubsection{Detailed Description}
Main program of the firmware execution.

\doxysubsubsection{Variable Documentation}
\Hypertarget{group__main_ga6bc19a77e2c149ca9b7e86d2ad25ef64}\label{group__main_ga6bc19a77e2c149ca9b7e86d2ad25ef64} 
\index{Firmware Tasks@{Firmware Tasks}!sampler\_timer\_conf@{sampler\_timer\_conf}}
\index{sampler\_timer\_conf@{sampler\_timer\_conf}!Firmware Tasks@{Firmware Tasks}}
\doxyparagraph{\texorpdfstring{sampler\_timer\_conf}{sampler\_timer\_conf}}
{\footnotesize\ttfamily const esp\+\_\+timer\+\_\+create\+\_\+args\+\_\+t sampler\+\_\+timer\+\_\+conf}

{\bfseries Initial value\+:}
\begin{DoxyCode}{0}
\DoxyCodeLine{=\ \{}
\DoxyCodeLine{\ \ \ \ \ \ \ \ .callback\ =\ \&isr\_sample}
\DoxyCodeLine{\}}

\end{DoxyCode}
\Hypertarget{group__main_gacb077cf1ef581c961e7e5222a98f6897}\label{group__main_gacb077cf1ef581c961e7e5222a98f6897} 
\index{Firmware Tasks@{Firmware Tasks}!stop\_timer\_conf@{stop\_timer\_conf}}
\index{stop\_timer\_conf@{stop\_timer\_conf}!Firmware Tasks@{Firmware Tasks}}
\doxyparagraph{\texorpdfstring{stop\_timer\_conf}{stop\_timer\_conf}}
{\footnotesize\ttfamily const esp\+\_\+timer\+\_\+create\+\_\+args\+\_\+t stop\+\_\+timer\+\_\+conf}

{\bfseries Initial value\+:}
\begin{DoxyCode}{0}
\DoxyCodeLine{=\ \{}
\DoxyCodeLine{\ \ \ \ .callback\ =\ \&stop\_timer\_run}
\DoxyCodeLine{\}}

\end{DoxyCode}

>>>>

\doxysubsection{firmware/main/src/main.c File Reference}
\hypertarget{main_8c}{}\label{main_8c}\index{firmware/main/src/main.c@{firmware/main/src/main.c}}
{\ttfamily \#include "{}pinout.\+h"{}}\newline
\doxysubsubsubsection*{Functions}
\begin{DoxyCompactItemize}
\item 
void {\bfseries push\+\_\+trigger} (void \texorpdfstring{$\ast$}{*}args)
\begin{DoxyCompactList}\small\item\em Task to start or stop recoding after siganl from button press. \end{DoxyCompactList}\item 
void {\bfseries read\+\_\+accelerometer} (void \texorpdfstring{$\ast$}{*}args)
\begin{DoxyCompactList}\small\item\em Task to read FIFO buffer of the accelerometer and write it to Queue. \end{DoxyCompactList}\item 
void {\bfseries write\+\_\+card} (void \texorpdfstring{$\ast$}{*}args)
\begin{DoxyCompactList}\small\item\em Task to write accelerations vectors from Queue to the memory card. \end{DoxyCompactList}\item 
void {\bfseries app\+\_\+main} (void)
\begin{DoxyCompactList}\small\item\em Entrypoint of firmware to setup hardware peripherals and run tasks. \end{DoxyCompactList}\end{DoxyCompactItemize}
\doxysubsubsubsection*{Variables}
\begin{DoxyCompactItemize}
\item 
Task\+Handle\+\_\+t {\bfseries trigger\+\_\+task}
\begin{DoxyCompactList}\small\item\em Task handler for notification of button press. \end{DoxyCompactList}\item 
Task\+Handle\+\_\+t {\bfseries sampler\+\_\+task}
\begin{DoxyCompactList}\small\item\em Task handler for notification from sampling timer. \end{DoxyCompactList}\item 
Queue\+Handle\+\_\+t {\bfseries samples}
\begin{DoxyCompactList}\small\item\em Queue for sending samples from the sensor read task to the memory card write task. \end{DoxyCompactList}\item 
spi\+\_\+device\+\_\+handle\+\_\+t {\bfseries spi}
\begin{DoxyCompactList}\small\item\em SPI bus handle. \end{DoxyCompactList}\item 
stmdev\+\_\+ctx\+\_\+t {\bfseries sensor}
\begin{DoxyCompactList}\small\item\em Accelerometer sensor device. \end{DoxyCompactList}\item 
sdmmc\+\_\+card\+\_\+t \texorpdfstring{$\ast$}{*} {\bfseries card} = NULL
\begin{DoxyCompactList}\small\item\em SD memory card handle. \end{DoxyCompactList}\item 
FILE \texorpdfstring{$\ast$}{*} {\bfseries file} = NULL
\begin{DoxyCompactList}\small\item\em Currently opened file handle. \end{DoxyCompactList}\item 
Semaphore\+Handle\+\_\+t {\bfseries file\+\_\+mutex}
\begin{DoxyCompactList}\small\item\em Mutex to protect file handle. \end{DoxyCompactList}\item 
bool {\bfseries is\+\_\+recording} = false
\begin{DoxyCompactList}\small\item\em Flag for active recording in progress. \end{DoxyCompactList}\item 
int32\+\_\+t {\bfseries sensor\+\_\+timestamp} = 0
\begin{DoxyCompactList}\small\item\em Last seen accelerometer timestamp. \end{DoxyCompactList}\item 
const esp\+\_\+timer\+\_\+create\+\_\+args\+\_\+t \mbox{\hyperlink{group__main_ga6bc19a77e2c149ca9b7e86d2ad25ef64}{sampler\+\_\+timer\+\_\+conf}}
\item 
esp\+\_\+timer\+\_\+handle\+\_\+t {\bfseries sampler\+\_\+timer}
\begin{DoxyCompactList}\small\item\em Periodic timer to signal when to read FIFO buffer from accelerometer. \end{DoxyCompactList}\item 
const esp\+\_\+timer\+\_\+create\+\_\+args\+\_\+t \mbox{\hyperlink{group__main_gacb077cf1ef581c961e7e5222a98f6897}{stop\+\_\+timer\+\_\+conf}}
\item 
esp\+\_\+timer\+\_\+handle\+\_\+t {\bfseries stop\+\_\+timer}
\begin{DoxyCompactList}\small\item\em Timer to stop recording after fixed amount of time. \end{DoxyCompactList}\end{DoxyCompactItemize}

\doxysubsubsection{Detailed Description}
Application setup

### 2024-05-13 thesis/chapters/01-introduction.tex
Thesis send to feedback

The chapter~\ref{chapter:evaluation} on evalution validates the classification accuracy of feature sets from MaFaulDa and strategies for their subset choice in the k-nearest neighbour model. The vibration signals in the realistic environment are also analysed and recommendations for practical application and further study are discussed.

>>>>

The chapter~\ref{chapter:evaluation} on evaluation validates the classification accuracy of feature sets from MaFaulDa and strategies for their subset choice in the k-nearest neighbour model. The vibration signals in the realistic environment are also analysed and recommendations for practical application and further study are discussed.

### 2024-05-13 thesis/chapters/02-analysis.tex
Complete evaluation
Thesis send to feedback

\subsection{Feature normalization}
Vibrations are measured with an accelerometer in the form of 3D vectors where each axis has its own component. Models have to be resilient to any slight inclination or sensor orientation. To satisfy this prerequisite, feature $f$ extracted from all three dimensions is first composed into a single vector and the Euclidian norm is computed~\cite{kamminga_robust_2018}.

\myequations{Feature euclidian norm}
\begin{ceqn}\begin{align}
\widetilde{f} = \sqrt{f_x^2 + f_y^2 + f_z^2}
\end{align}\end{ceqn}

@@

\emph{Pearson correlation} coeficient expresses similarity between two quantitative features: $f_i$ and $f_j$. In the classification setting, the correlation of feature $f$ makes sense only with dichotomous target class label $c$ using \emph{point biserial coeficient}. Mathematically, this is equivalent to the Pearson coefficient. Rank correspondence is quantified with either Spearman rho or Kendall's Tau~\cite{calkins_more_2005}.

\begin{table}[ht]
\renewcommand{\arraystretch}{1.5}
\begin{adjustbox}{width=\columnwidth,center}
\begin{tabular}{|c|l|l|l|}
\hline
\textbf{Variable Y\textbackslash{}X} & \multicolumn{1}{c|}{\textbf{Quantitiative X}} & \multicolumn{1}{c|}{\textbf{Ordinal X}} & \multicolumn{1}{c|}{\textbf{Nominal X}} \\ \hline
\textbf{Quantitative Y}              & Pearson $r$                                   & Biserial $r_b$                          & Point Biserial $r_{pb}$                 \\ \hline
\textbf{Ordinal Y}                   & Biserial $r_b$                                & Spearman $\rho$    & Rank Biserial $r_{rb}$                  \\ \hline
\textbf{Nominal Y}                   & Point Biserial $r_{pb}$                       & Rank Bisereal $r_{rb}$                  & Phi, L, C, Lambda                       \\ \hline
\end{tabular}
\end{adjustbox}
\caption{Correlation coeficients}
\label{tab:corr-coef}
\end{table}

@@

\item \textbf{Mutal information} - quantifies the dependence between features, or between features and class labels. It is almost identical to Information Gain. The probability distribution of proximity of variables derives from the relative entropy known as the Kullback-Leibler distance. Mutual information presumes variables are discrete. In the case of quantitative variables, mutual information is estimated by binning or nearest neighbours methods~\cite{ross_mutual_2014}.

@@

\myequations{Mutal information}
\begin{ceqn}\begin{align}
\mathrm{MI}(X, Y) = \sum_{y \in Y} \sum_{x \in X} P(x, y) \cdot \log\left(\frac{P(x, y)}{P(x)P(y)}\right)
\end{align}\end{ceqn}
\end{itemize}

@@

The meaning of distance between feature vectors $\mathbf{x}$, $\mathbf{y}$ have to be defined, so several metrics are available like \emph{Euclidian distance}, \emph{Mahalanobis distance}, \emph{Manhatann distance} etc. (Tab.~\ref{tab:KNN-distance})~\cite{sheng_review_2020, abu_alfeilat_effects_2019}. The optimal $k$ parameter is set by supervised learning according to the breaking point in the elbow curve that plots choices of $k$ against the error rate. The demanding neighbourhood queries are sped up using spatial indexes in databases that utilize search trees such as kd-tree, R-tree, or M-tree.

\begin{table}[ht]
\centering
\renewcommand{\arraystretch}{2}
\begin{tabular}{|l|l|}
\hline
\textbf{Distance}     & \textbf{$d(\mathbf{x}, \mathbf{y})$}                                   \\ \hline
Manhattan distance	 & $ |x_i - y_i| $													   \\ \hline
Euclidian distance    & $ \sqrt{\sum_{i = 1}^{n}(x_i - y_i)^2} $                               \\ \hline
Mahalanobis distance  & $ (\mathbf{x} - \mathbf{y})^T C^{-1} (\mathbf{x} - \mathbf{y}) $       \\ \hline
\end{tabular}
\caption{Distance metrics for k-NN}
\label{tab:KNN-distance}
\end{table}

>>>>

\subsection{Feature normalization}
Vibrations are measured with an accelerometer in the form of 3D vectors where each axis has its own component. Models have to be resilient to any slight inclination or sensor orientation. To satisfy this prerequisite, feature $f$ extracted from all three dimensions is first composed into a single vector and the Euclidean norm is computed~\cite{kamminga_robust_2018}.

\myequations{Feature euclidean norm}
\begin{ceqn}\begin{align}
\widetilde{f} = \sqrt{f_x^2 + f_y^2 + f_z^2}
\end{align}\end{ceqn}

@@

\emph{Pearson correlation} coefficient expresses similarity between two quantitative features: $f_i$ and $f_j$. In the classification setting, the correlation of feature $f$ makes sense only with dichotomous target class label $c$ using \emph{point biserial coefficient}. Mathematically, this is equivalent to the Pearson coefficient. Rank correspondence is quantified with either Spearman rho or Kendall's Tau~\cite{calkins_more_2005}.

\begin{table}[ht]
\renewcommand{\arraystretch}{1.5}
\begin{adjustbox}{width=\columnwidth,center}
\begin{tabular}{|c|l|l|l|}
\hline
\textbf{Variable Y\textbackslash{}X} & \multicolumn{1}{c|}{\textbf{Quantitiative X}} & \multicolumn{1}{c|}{\textbf{Ordinal X}} & \multicolumn{1}{c|}{\textbf{Nominal X}} \\ \hline
\textbf{Quantitative Y}              & Pearson $r$                                   & Biserial $r_b$                          & Point Biserial $r_{pb}$                 \\ \hline
\textbf{Ordinal Y}                   & Biserial $r_b$                                & Spearman $\rho$    & Rank Biserial $r_{rb}$                  \\ \hline
\textbf{Nominal Y}                   & Point Biserial $r_{pb}$                       & Rank Bisereal $r_{rb}$                  & Phi, L, C, Lambda                       \\ \hline
\end{tabular}
\end{adjustbox}
\caption{Correlation coefficients}
\label{tab:corr-coef}
\end{table}

@@

\item \textbf{Mutual information} - quantifies the dependence between features, or between features and class labels. It is almost identical to Information Gain. The probability distribution of proximity of variables derives from the relative entropy known as the Kullback-Leibler distance. Mutual information presumes variables are discrete. In the case of quantitative variables, mutual information is estimated by binning or nearest neighbours methods~\cite{ross_mutual_2014}.

@@

\myequations{Mutual information}
\begin{ceqn}\begin{align}
\mathrm{MI}(X, Y) = \sum_{y \in Y} \sum_{x \in X} P(x, y) \cdot \log\left(\frac{P(x, y)}{P(x)P(y)}\right)
\end{align}\end{ceqn}
\end{itemize}

@@

The meaning of distance between feature vectors $\mathbf{x}$, $\mathbf{y}$ have to be defined, so several metrics are available like \emph{Euclidean distance}, \emph{Mahalanobis distance}, \emph{Manhatann distance} etc. (Tab.~\ref{tab:KNN-distance})~\cite{sheng_review_2020, abu_alfeilat_effects_2019}. The optimal $k$ parameter is set by supervised learning according to the breaking point in the elbow curve that plots choices of $k$ against the error rate. The demanding neighbourhood queries are sped up using spatial indexes in databases that utilize search trees such as kd-tree, R-tree, or M-tree.

\begin{table}[ht]
\centering
\renewcommand{\arraystretch}{2}
\begin{tabular}{|l|l|}
\hline
\textbf{Distance}     & \textbf{$d(\mathbf{x}, \mathbf{y})$}                                   \\ \hline
Manhattan distance	 & $ |x_i - y_i| $													   \\ \hline
Euclidean distance    & $ \sqrt{\sum_{i = 1}^{n}(x_i - y_i)^2} $                               \\ \hline
Mahalanobis distance  & $ (\mathbf{x} - \mathbf{y})^T C^{-1} (\mathbf{x} - \mathbf{y}) $       \\ \hline
\end{tabular}
\caption{Distance metrics for k-NN}
\label{tab:KNN-distance}
\end{table}
